\documentclass[10pt]{article}

\usepackage[margin=0.15in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}

% Compact list settings
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=0.14in}

% Section header formatting (smaller)
\newcommand{\sectionTitle}[1]{\vspace{1pt}\noindent\textbf{\small #1}\vspace{0.5pt}\hrule\vspace{1pt}}

\begin{document}
\small

% -------------------------
% HEADER
% -------------------------
\begin{center}
    {\large \textbf{Suhas Kowligi}}\\
    DFW, TX \;|\; (682) 406-8550 \;|\; \href{mailto:suhasbk42@gmail.com}{suhasbk42@gmail.com}\\
    \href{https://www.linkedin.com/in/suhas-kowligi-b39a9415a}{LinkedIn} \;|\;
    \href{https://github.com/SuhasBk}{GitHub} \;|\;
    \href{https://suhasbk.github.io}{Portfolio}
\end{center}

% -------------------------
% SUMMARY
% -------------------------
\sectionTitle{SUMMARY}

Full Stack Engineer and MSCS graduate (GPA 3.9) with 4+ years of experience designing cloud-native services, microservices, and scalable backend systems. Proficient in \textbf{Java/Spring Boot}, \textbf{Azure}, \textbf{Terraform}, \textbf{Docker}, \textbf{Kubernetes}, and SQL optimization. Delivered high-impact architectural improvements that improved deployment frequency by \textbf{70\%} and reduced system latency by \textbf{30\%}.

% -------------------------
% EXPERIENCE
% -------------------------
\sectionTitle{EXPERIENCE}

\textbf{Toshiba Global Commerce Solutions} \hfill Frisco, TX \\
\textit{Software Engineer I (Full-Time)} \hfill May 2025 -- Present
\begin{itemize}
    \item Increased deployment frequency by \textbf{70\%} by refining \textbf{Terraform} parameters and supporting migration from single-tenant to multi-tenant architecture.
    \item Resolved persistent Out-Of-Memory (OOM) issues in \textbf{AKS} microservices, tuned Horizontal Pod Autoscaler (\textbf{HPA}) configurations, and optimized \textbf{JVM} resource usage, improving service reliability by \textbf{25\%}.
    \item Automated secure creation of \textbf{Azure Service Principals} and \textbf{Key Vault} secret ingestion, reducing manual setup time across teams by \textbf{40\%}.
    \item Enhanced internal deployment UI workflows, enabling faster and more reliable product releases.
\end{itemize}

\textit{Cloud Engineer Intern} \hfill May 2024 -- May 2025
\begin{itemize}
    \item Developed cloud deployment platform using \textbf{Azure Durable Functions}, integrating Azure Spring Apps, Static Web Apps, and Azure SQL Server.
    \item Built \textbf{Docker}-based service health monitors using Uptime Kuma, enabling proactive detection and resolution of degraded or failed cloud resources, reducing downtime by \textbf{20\%}.
    \item Authored reusable \textbf{Terraform IaC} modules and \textbf{Jenkins} pipelines, standardizing cloud provisioning and artifact generation.
    \item Implemented \textbf{Azure Service Bus} messaging for new user registrations, ensuring reliable automated onboarding workflows.
\end{itemize}

\textbf{Brillio} \hfill Bangalore, India \\
\textit{Senior Software Engineer} \hfill Apr 2022 -- Aug 2023
\begin{itemize}
    \item Led a 4-member team to deliver high-performance RFDS \textbf{REST APIs} for a major U.S. telecom provider.
    \item Reduced API latency by \textbf{30\%} through \textbf{PL/SQL} optimization and multithreading with ExecutorService and Callable.
    \item Automated operational workflows with \textbf{Bash + CRON}, saving \textbf{10+ engineer-hours} per week.
    \item Improved backend reliability and UI performance through caching strategies and structured refactoring.
\end{itemize}

\textit{Product Engineer} \hfill Sep 2020 -- Apr 2022
\begin{itemize}
    \item Built full-stack features using \textbf{Spring Boot}, Java EE, jQuery, and Oracle SQLDeveloper.
    \item Reduced customer issues by \textbf{40\%} via API optimizations and root-cause analysis of production incidents.
\end{itemize}

% -------------------------
% PROJECTS
% -------------------------
\sectionTitle{PROJECTS}

\textbf{RAG Pipeline for Document Q\&A} \hfill \href{https://github.com/SuhasBk/doc_kb_RAG}{GitHub}
\begin{itemize}
    \item Enabled faster domain-specific Q\&A over PDFs by implementing recursive chunking and embedding optimizations using \textbf{nomic-embed-text}, improving processing efficiency by \textbf{50\%}.
    \item Built the pipeline using \textbf{LangChain}, \textbf{ChromaDB}, and \textbf{Phi-3 (Ollama)}.
\end{itemize}

\textbf{Microservices Greeting Card App} \hfill \href{https://github.com/SuhasBk/vcard-microservices}{GitHub}
\begin{itemize}
    \item Built a full-stack microservice architecture, improving service modularity and scalability.
    \item Integrated Giphy API and \textbf{MongoDB Atlas} for centralized data storage, with a \textbf{React} frontend.
\end{itemize}

\textbf{Walkie-Talkie (WebSockets)} \hfill \href{https://walkie-talkie.fly.dev}{Demo}
\begin{itemize}
    \item Developed a real-time browser-based voice chat app, supporting concurrent client sessions with low latency.
    \item Captured and played back audio using Web Audio API and MediaRecorder; backend implemented with \textbf{Spring Boot WebSockets} and binary streaming.
\end{itemize}

\textbf{ASL Recognition (Computer Vision)}
\begin{itemize}
    \item Achieved \textbf{96\% accuracy} for real-time ASL alphabet recognition using a \textbf{PyTorch} deep learning model.
    \item Optimized the training pipeline with data augmentation and adaptive learning rates to outperform baseline models like AlexNet.
\end{itemize}

\textbf{ePapers Web Application} \hfill \href{https://epapers.fly.dev}{Demo}
\begin{itemize}
    \item Streamlined access to local newspaper PDFs, integrating \textbf{MongoDB}, OAuth, and Telegram Bots.
    \item Applied \textbf{Strategy Design Pattern} to handle subscription logic and scalability.
\end{itemize}

\textbf{ML-based Ensemble Network Security System} \hfill \href{https://link.springer.com/chapter/10.1007/978-981-16-3342-3_1}{Springer Link}
\begin{itemize}
    \item Detected malicious network packets using ML algorithms (Naive Bayes, K-NN, Decision Tree), improving security monitoring efficiency.
    \item Authored and published a research paper in the \textbf{Springer Journal} (November 2021).
    \item Implemented scripts with \textbf{Python} and iptables for automated threat mitigation.
\end{itemize}

\textbf{Lord of the Rings (LOTR) Design Patterns} \hfill \href{https://github.com/SuhasBk/LOTR---Design-Patterns}{GitHub}
\begin{itemize}
    \item Applied object-oriented design patterns (\textbf{Strategy, Adapter, Command, Decorator, Factory}) to model complex LOTR-themed scenarios.
    \item Improved code reusability and maintainability by implementing modular and extensible solutions.
\end{itemize}

\textbf{LibSeat Automation} \hfill \href{https://libseat.fly.dev}{Demo}
\begin{itemize}
    \item Reduced manual steps in study room reservations by \textbf{90\%} by automating the workflow with a \textbf{Python Flask} web app.
    \item Simplified user interactions with an intuitive interface and streamlined backend logic.
\end{itemize}

% -------------------------
% SKILLS
% -------------------------
\sectionTitle{SKILLS}

\textbf{Languages:} Java, Python, JavaScript, SQL, C, Bash \\
\textbf{Frameworks \& Libraries:} Spring Boot, Hibernate, React, Flask, jQuery, Selenium, JUnit, PyTorch, TensorFlow, LangChain, NumPy, Pandas \\
\textbf{Databases:} PostgreSQL, Oracle PL/SQL, MongoDB, MySQL, SQL Server \\
\textbf{Tools \& Platforms:} Azure, Docker, Kubernetes, Terraform, Jenkins, Git, Linux, Kafka, NGINX, Maven, Nexus, SonarQube, JIRA, WebSocket, JSON, YAML

% -------------------------
% CERTIFICATIONS
% -------------------------
\sectionTitle{CERTIFICATIONS}

Microsoft Azure Fundamentals (AZ-900) \;|\; Scaled Agile Framework (SAFe 5) Practitioner

% -------------------------
% EDUCATION
% -------------------------
\sectionTitle{EDUCATION}

\textbf{University of Texas at Arlington} \hfill Arlington, TX \\
Master of Science, Computer Science — \textbf{GPA: 3.9} \hfill 2025

\textbf{Nitte Meenakshi Institute of Technology} \hfill Bangalore, India \\
Bachelor of Engineering, Information Science — GPA 3.68 \hfill 2020

\end{document}