\documentclass[10pt]{article}

\usepackage[margin=0.25in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}

% Compact list settings
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=0.17in}

% Section header formatting (simple, built-in)
\newcommand{\sectionTitle}[1]{\vspace{3pt}\noindent\textbf{\small #1}\vspace{1pt}\hrule\vspace{3pt}}

\begin{document}
\small % <-- All text below this line is smaller

% -------------------------
% HEADER
% -------------------------
\begin{center}
    {\Large \textbf{Suhas Kowligi}}\\
    DFW, TX \;|\; (682) 406-8550 \;|\; \href{mailto:suhasbk42@gmail.com}{suhasbk42@gmail.com}\\
    \href{https://www.linkedin.com/in/suhas-kowligi-b39a9415a}{LinkedIn} \;|\;
    \href{https://github.com/SuhasBk}{GitHub} \;|\;
    \href{https://suhasbk.github.io}{Portfolio}
\end{center}

% -------------------------
% SUMMARY
% -------------------------
% \sectionTitle{SUMMARY}

% Highly skilled Java Backend Engineer with 4+ years of experience in designing, developing, and deploying robust, scalable microservices and web applications. Proficient in Java 8+, Spring Boot, Spring Cloud, Hibernate, RESTful APIs, and secure development practices. Proven ability to optimize backend systems, integrate diverse databases (SQL/NoSQL), and leverage cloud platforms (Azure) and CI/CD tools (Jenkins, Maven) to deliver high-performance solutions.

% -------------------------
% EXPERIENCE
% -------------------------
\sectionTitle{EXPERIENCE}

\textbf{Toshiba Global Commerce Solutions} \hfill Frisco, TX \\
\textit{Software Engineer I (Full-Time)} \hfill May 2025 -- Present
\begin{itemize}
    \item Resolved persistent Out-Of-Memory (OOM) issues in AKS microservices, tuned Horizontal Pod Autoscaler (HPA) configurations, and optimized JVM resource usage, improving service reliability by 25\%.
    \item Automated secure creation of Azure Service Principals and Key Vault secret ingestion, reducing manual setup time across teams by 40\%, adhering to secure development best practices.
    \item Increased deployment frequency by 70\% by refining Terraform parameters and supporting migration from single-tenant to multi-tenant architecture on Azure.
    \item Enhanced internal deployment UI workflows, enabling faster and more reliable product releases through continuous integration practices.
\end{itemize}

\textit{Cloud Engineer Intern} \hfill May 2024 -- May 2025
\begin{itemize}
    \item Developed cloud deployment platform using Azure Durable Functions, integrating Azure Spring Apps, Static Web Apps, and Azure SQL Server.
    \item Authored reusable Terraform IaC modules and Jenkins pipelines, standardizing cloud provisioning and artifact generation for Java applications.
    \item Built Docker-based service health monitors using Uptime Kuma, enabling proactive detection and resolution of degraded or failed cloud resources, reducing downtime by 20\%.
    \item Implemented Azure Service Bus messaging for new user registrations, ensuring reliable automated onboarding workflows.
\end{itemize}

\textbf{Brillio} \hfill Bangalore, India \\
\textit{Senior Software Engineer} \hfill Apr 2022 -- Aug 2023
\begin{itemize}
    \item Led a 4-member team to deliver high-performance RFDS REST APIs for a major U.S. telecom provider, focusing on Domain Driven Design.
    \item Reduced API latency by 30\% through PL/SQL optimization and multithreading with Java's ExecutorService and Callable, enhancing backend performance.
    \item Improved backend reliability and UI performance through caching strategies and structured refactoring of Java services.
    \item Automated operational workflows with Bash + CRON, saving 10+ engineer-hours per week.
\end{itemize}

\textit{Product Engineer} \hfill Sep 2020 -- Apr 2022
\begin{itemize}
    \item Built full-stack features using Spring Boot, Java EE, jQuery, and Oracle SQLDeveloper, demonstrating strong web and backend application development skills.
    \item Reduced customer issues by 40\% via API optimizations and root-cause analysis of production incidents, ensuring robust backend operations.
\end{itemize}

% -------------------------
% PROJECTS
% -------------------------
\sectionTitle{PROJECTS}

\textbf{Microservices Greeting Card App} \hfill \href{https://github.com/SuhasBk/vcard-microservices}{GitHub}
\begin{itemize}
    \item Built a full-stack microservice architecture with a React frontend, integrating Giphy API and MongoDB Atlas for scalable data storage and improved service modularity.
\end{itemize}

\textbf{ePapers Web Application} \hfill \href{https://epapers.fly.dev}{Demo}
\begin{itemize}
    \item Developed and deployed a Java Spring Boot web application for accessing public PDFs, applying Strategy design pattern for scalability and integrating MongoDB, OAuth, and Telegram Bots.
\end{itemize}

\textbf{Walkie-Talkie (WebSockets)} \hfill \href{https://walkie-talkie.fly.dev}{Demo}
\begin{itemize}
    \item Developed a real-time browser-based voice chat application using Spring Boot WebSockets with binary streaming, supporting concurrent client sessions and low-latency audio capture/playback.
\end{itemize}

% -------------------------
% SKILLS
% -------------------------
\sectionTitle{SKILLS}

\textbf{Languages:} Java (8+), Python, JavaScript, SQL, C, Bash \\
\textbf{Frameworks \& Libraries:} Spring Boot, Spring Cloud, Hibernate, Spring Security, Spring MVC, Spring Integration, JUnit, REST, React, Flask, jQuery
\textbf{Databases:} PostgreSQL, Oracle PL/SQL, MongoDB, MySQL, SQL Server \\
\textbf{Tools \& Platforms:} Azure, Docker, Kubernetes, Terraform, Jenkins, Git, Linux, Kafka, NGINX, Maven, Nexus, SonarQube, JIRA, WebSocket, JSON, YAML

% -------------------------
% CERTIFICATIONS
% -------------------------
\sectionTitle{CERTIFICATIONS}

Microsoft Azure Fundamentals (AZ-900) \;|\; Scaled Agile Framework (SAFe 5) Practitioner

% -------------------------
% EDUCATION
% -------------------------
\sectionTitle{EDUCATION}

\textbf{University of Texas at Arlington} \hfill Arlington, TX \\
Master of Science, Computer Science — GPA: 3.9 \hfill 2025

\textbf{Nitte Meenakshi Institute of Technology} \hfill Bangalore, India \\
Bachelor of Engineering, Information Science — GPA 3.68 \hfill 2020

\end{document}